---
title: "Brownlows Bets"
author: "Demian Romero"
date: "10/16/19"
output: html_document: default
 ---

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 1137 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 1137 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

We are going to set up a dataset of birthdays containing all the days of the year. Then we will use an R function to randomly sample with replacement of 35. If 2 samples are the same we will add $1 to the Brownlow Bank, and if not we will subtract $2. We wil repeat this excercise 1,137 times. We will then draw a histogram of all the winnings, and remove 2.5% from the top and another 2.5% from the bottom scores, resulting in a 95% confidance interval.

# Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting!-->
First we create the year data and a vector to contain samples. Then we set up a bank of 0. 

```{r}
Bdays = 1:356
Bsamples = vector ('numeric')
TotalDollars = 0
saveDollars=vector('numeric')
```

Then I am going to run the simulation 1137 times.

```{r}

for (loop in 1:1000){
TotalDollars=0 
classSize = 35
for(i in 1:1137) { 
Bsamples= sample(Bdays, classSize, replace=TRUE) 
if (length(unique(Bsamples)) == 35) { 
TotalDollars = TotalDollars -2
} else {
  TotalDollars = TotalDollars +1
}
}
saveDollars [loop] = TotalDollars}


hist(saveDollars)
print (mean(saveDollars))
```



# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows-->


```{r}
stdevDollars = sd(saveDollars)
meandollars = mean(saveDollars)
CI = c(meandollars-2*stdevDollars, meandollars+2*stdevDollars)

print (CI)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

With a class size of 35, the is a 95% confidance that each sampling will come in with a profit between $453.86 and $606.82 per bet.
 
If we change the payouts to +$1 if he wins and -$4.50 if he loses Professor Brownlow would break even on his bets.

In order to have his payout equal $0 Prfessor Brownlow would need to change his class size to between 28 and 29 students, the actual number would be between the two numbers, but you cannot have a partial student. 

